---
title: "p8105_hw1_yz4717"
author: "Yang Zhao__yz4717"
date: "2023-09-18"
output: html_document
---

First, we have to install the package(the code will be displayed and won't excuted).

```{r installpk,eval=FALSE}
install.packages("moderndive")
```

Then, I input the data which was mentioned in the problem and all the needed packages.

```{r input}
library(moderndive)
library(tidyverse)
library(ggplot2)
data("early_january_weather")
```

## Problem 1

As mentioned, we can use the function "names()" to list all the variables.

```{r}
names(early_january_weather)
```
All names of vectors are shown above.

```{r}
shape_row = nrow(early_january_weather)
shape_col = ncol(early_january_weather)
```
The dataset contains `r shape_row` Rows * `r shape_col` Columns.
```{r}
rs_mean = mean(early_january_weather$temp)
```
And calculation of mean of temperature are shown, so the result is `r rs_mean`.
Then, I used the ggplot function to generate a scatterplot of tempureture and time

```{r}
time_temp_tib = tibble(
  time = pull(early_january_weather,time_hour),
  temp = pull(early_january_weather,temp),
  humid = pull(early_january_weather,humid)
)

plot_sc = 
  ggplot(
  data = time_temp_tib
)+geom_point(
  mapping = aes(
    x = time,
    y = temp,
    color = humid)
)
plot_sc
```
I prefer to pull out all the needed vectors and make a new table for them. After that, I used ggplot function to generate a scatterplot (x-axis - time_hour, y-axis - temp). There are ups and downs in the graph. 



```{r}
ggsave("sc_plot.png",device = "png")
```


##Problem 2

Then, I generated a random sample of size 10 from normal distribution.

```{r}
vc_norm = rnorm(10,mean = 0,sd = 1)

vc_logic = vc_norm > 0

vc_char = c("a","b","c","d","e","f","g","h","i","j")

vc_fac = factor(
  c("Low", "Medium", "Low", "High", "Medium",
    "Low", "High","Medium", "Low", "High"))

combined_frame = data.frame(
  normal_distri = vc_norm,
  logical_vc = vc_logic,
  character_vc = vc_char,
  factor_vc = vc_fac
)
```

I created a random sample for standard normal distribution(mean = 0, sd = 1), and the result are shown above.


