---
title: "p8105_hw1_yz4717"
author: "Yang Zhao__yz4717"
date: "2023-09-18"
output: html_document
---

First, we have to install the package(the code will be displayed and won't excuted).

```{r installpk,eval=FALSE}
install.packages("moderndive")
```

Then, I input the data which was mentioned in the problem.

```{r input}
library(moderndive)
library(tidyverse)
library(ggplot2)
data("early_january_weather")
```

## Problem 1

As mentioned, we can use the function "names()" to list all the variables.

```{r}
names(early_january_weather)
```
All names of vectors are shown above.

```{r}
shape_row = nrow(early_january_weather)
shape_col = ncol(early_january_weather)
```
The dataset contains `r shape_row` Rows * `r shape_col` Columns.
```{r}
rs_mean = mean(early_january_weather$temp)
```
And calculation of mean of temperature are shown, so the result is `r rs_mean`.
Then, I used the ggplot function to generate a scatterplot of tempureture and time

```{r}
time_temp_tib = tibble(
  time = pull(early_january_weather,time_hour),
  temp = pull(early_january_weather,temp),
  humid = pull(early_january_weather,humid)
)

ggplot(
  data = time_temp_tib
)+geom_point(
  mapping = aes(
    x = time,
    y = temp,
    color = humid)
)
```
I prefer to pull out all the needed vectors and make a new table for them. After that, I used ggplot function to generate a scatterplot (x-axis - time_hour, y-axis - temp)



```{r}
ggsave(path = "scatterplot.pdf")
```

