---
title: "p8105_hw1_yz4717"
author: "Yang Zhao__yz4717"
date: "2023-09-18"
output: html_document
---

First, we have to install the package(the code will be displayed and won't excuted).

```{r installpk,eval=FALSE}
install.packages("moderndive")
```

Then, I input the data which was mentioned in the problem and all the needed packages.

```{r input}
library(moderndive)
library(tidyverse)
library(ggplot2)
data("early_january_weather")
```

## Problem 1

As mentioned, we can use the function "names()" to list all the variables.

```{r list_name}
names(early_january_weather)
```
All names of vectors are shown above.

```{r shape}
shape_row = nrow(early_january_weather)
shape_col = ncol(early_january_weather)
```
The dataset contains `r shape_row` Rows * `r shape_col` Columns.
```{r cal_mean}
rs_mean = mean(early_january_weather$temp)
```
And calculation of mean of temperature are shown, so the result is `r rs_mean`.
Then, I used the ggplot function to generate a scatterplot of tempureture and time

```{r pull_plot}
time_temp_tib = tibble(
  time = pull(early_january_weather,time_hour),
  temp = pull(early_january_weather,temp),
  humid = pull(early_january_weather,humid)
)

plot_sc = 
  ggplot(
  data = time_temp_tib
)+geom_point(
  mapping = aes(
    x = time,
    y = temp,
    color = humid)
)
plot_sc
```
I prefer to pull out all the needed vectors and make a new table for them. After that, I used ggplot function to generate a scatterplot (x-axis - time_hour, y-axis - temp). There are ups and downs in the graph. 



```{r save_plot}
ggsave("sc_plot.png",device = "png")
```


##Problem 2

Then, I generated a random sample of size 10 from normal distribution.

```{r create_df}
vc_norm = rnorm(10,mean = 0,sd = 1)

vc_logic = vc_norm > 0

vc_char = c("a","b","c","d","e","f","g","h","i","j")

vc_fac = factor(
  c("Low", "Medium", "Low", "High", "Medium",
    "Low", "High","Medium", "Low", "High"))

combined_frame = data.frame(
  normal_distri = vc_norm,
  logical_vc = vc_logic,
  character_vc = vc_char,
  factor_vc = vc_fac
)
```

I created a random sample for standard normal distribution(mean = 0, sd = 1),a logical vector, a character vector and a  and the result are shown above.

```{r test_mean}
mean_1 = mean(vc_norm)
mean_2 = mean(vc_logic)
mean_3 = mean(vc_char)
mean_4 = mean(vc_fac)

mean_rs = list(mean_1,mean_2,mean_3,mean_4)
mean_rs
```

As the question mentioned, I used the "mean()" function to calculate average. As you can see, this function can calculate the mean of numeric and logical vector. It is obvious that it can calculate numeric vector and can not calculate character vector. When it comes to logical vector, we can still get a result, just because the logical value is a simple '0' or '1' in the computer(which stands for 'False' or 'True' respectively).
